The Courtroom Challenge\\\large Can Any Open-World AI Thrive Without Paying the Validation Bill?\\[1em]\small\textit{This note poses a conjecture, not a leaderboard: automate validation, prove it's unnecessary, or price human judgment honestly.}

### 2025-05-05 main.tex
Update contact
Update git repo

% ---------- title data ----------
\title{The Courtroom Challenge\\\large Can Any Open-World AI Thrive Without Paying the Validation Bill?\\[1em]\small\textit{This note poses a conjecture, not a leaderboard: automate validation, prove it's unnecessary, or price human judgment honestly.}}
\author{John Repsys\thanks{email: contact@johnrepsys.com}}
\date{\today}

@@

% =========================================================
\begin{document}
\maketitle
\begin{abstract}
  Large language models hallucinate; ad-hoc patches conceal the true cost of verification. We therefore pose the Courtroom Challenge:
  Conjecture 1. For any unbounded open-world text stream, a system that lacks both (i) a persistent precedent store and (ii) a friction-priced validation loop will accumulate unbounded prequential regret.
  We formalise the state machine, cost ledger, and impossibility triangle that make this conjecture falsifiable, and invite the community to break it. A 100-query toy stream illustrates how the ledger is logged\footnote{Baseline script will appear at github.com/johnrepsys/courtroom-challenge with v2.}; no attempt is made here to optimise the validator. In addition, we present the Courtroom Model, a wrapper architecture that subjects every LLM claim to a perpetual cycle of precedent search, automated semantic checks, and selective escalation to an external judge—human or automated. Each new output is validated against a persistent vector memory, while conflicting evidence triggers the re-examination of prior “case law.”
\end{abstract}

>>>>

% ---------- title data ----------
\title{The Courtroom Challenge\\\large Can Any Open-World AI Thrive Without Paying the Validation Bill?\\[1em]\small\textit{This note poses a conjecture, not a leaderboard: automate validation, prove it's unnecessary, or price human judgment honestly.}}
\author{John Repsys\thanks{email: john.repsys@gmail.com}}
\date{\today}

@@

% =========================================================
\begin{document}
\maketitle
\begin{abstract}
  Large language models hallucinate; ad-hoc patches conceal the true cost of verification. We therefore pose the Courtroom Challenge:
  Conjecture 1. For any unbounded open-world text stream, a system that lacks both (i) a persistent precedent store and (ii) a friction-priced validation loop will accumulate unbounded prequential regret.
  We formalise the state machine, cost ledger, and impossibility triangle that make this conjecture falsifiable, and invite the community to break it. A 100-query toy stream illustrates how the ledger is logged\footnote{Baseline script will appear at github.com/johnrepsys/courtroom-model-lean with v2.}; no attempt is made here to optimise the validator. In addition, we present the Courtroom Model, a wrapper architecture that subjects every LLM claim to a perpetual cycle of precedent search, automated semantic checks, and selective escalation to an external judge—human or automated. Each new output is validated against a persistent vector memory, while conflicting evidence triggers the re-examination of prior “case law.”
\end{abstract}
